---
title: "Shiny Assignment"
author: "Vipul Sharma"
date: "2/19/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, warning=FALSE, message=FALSE}
library(plotly)
library(dplyr)
population <- read.csv("pop_India.csv",stringsAsFactors = FALSE)
```

## Plotly Assignment

This presentation is prepared to demonstrate Shiny use in generating data prodcuts.

Here the data has been taken from https://www.livepopulation.com and selected India as country. The data demonstrates current india population and sex ratios

## A view at the Data

```{r, comment=""}
head(population)
```

## The Plot

```{r}
colorMale <- rep('rgba(204,204,204,1)',21)
colorFemale <- rep('rgba(224,204,214,1)',21)

p <- plot_ly(population, x = ~Age, y = ~Male...., type = 'bar', name = 'Males Percentage',marker = list(color =colorMale)) %>%
            add_trace(y = ~Female...., name = 'Females Percentage', marker = list(color =colorFemale)) %>%
            layout(yaxis = list(title = 'Sex Ratio'), barmode = 'group') %>%
            layout(xaxis = list(type = "category"))
p
```

## The Application

Now the Application helps you select the topmost male and female population using the two sliders and based on selection the plot gets those highlighted in RED colour.

We can also see the selected population values as well.